Appendix for "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2025-01-22 manuscript/appendix.qmd
Show more of TOC

---
title: 'Appendix for "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"'
short-title: 'Appendix for "Why Donors Donate"'
date: "2025-01-20"
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
  orcid: 0000-0003-3506-7590
- name: Marc Dotson
  affiliation: Utah State University
  url: https://occasionaldivergences.com/
  email: marc.dotson@usu.edu
  orcid: 0000-0001-7846-3660
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
  attributes:
    corresponding: true
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
bibliography: references.bib
csl: csl/apa.csl
link-citations: true
crossref: 
  tbl-title: "Table&nbsp;A"
  fig-title: "Figure&nbsp;A"
toc: true
toc-depth: 3
format: 
  html: default
  hikmah-pdf:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
  hikmah-manuscript-pdf+ms:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
---

>>>>

---
title: 'Appendix for "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"'
short-title: 'Appendix for "Why Donors Donate"'
date: "2025-01-22"
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
  orcid: 0000-0003-3506-7590
- name: Marc Dotson
  affiliation: Utah State University
  url: https://occasionaldivergences.com/
  email: marc.dotson@usu.edu
  orcid: 0000-0001-7846-3660
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
  attributes:
    corresponding: true
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
bibliography: references.bib
csl: csl/apa.csl
link-citations: true
crossref: 
  tbl-title: "Table&nbsp;A"
  fig-title: "Figure&nbsp;A"
toc: true
toc-depth: 4
format: 
  html: default
  hikmah-pdf:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
  hikmah-manuscript-pdf+ms:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
---
